---
title: "realEstateDictionaries"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{realEstateDictionaries}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading the data
The **listings** data set includes 24,446 listings from Atlanta, GA.  The data set includes the price, square footage of living space, and public remarks about the property.

```{r realEstateDictionaries}
library(realEstateDictionaries)
data(listings)
str(listings)
```

## Cleaning the Text
The **cleanText** function cleans the text by removing punctuation, numerical values, and stop words from the text.  The raw text

```{r message=FALSE, warning=FALSE}
text0 <- head(listings$remarks , n=3)
text0
```

The cleaned text

```{r message=FALSE, warning=FALSE}
text1 <- cleanText(text0)
text1
```

Other options are available in the options of **cleanText**

```{r message=FALSE, warning=FALSE}
text2 <- cleanText(text0 , removeStopWords = FALSE)
text2
```

## Creating a Token Matrix
You can also create a matrix $M$ of indicator variables for the $n$-gram tokens.  A token is a sequence of $n$ consecutive phrases.  The $n=1$ or unigram corresponds to single words.  The $n=2$ or bigram corresponds to two-word phrases.  **tokenMatrixMaker** can handle up to $n=3$ or trigrams.  You can specify $n$ using **GRAM**. The default is 1-grams.  

```{r message=FALSE, warning=FALSE}
M1 <- tokenMatrixMaker(text1)
head(M1)
colnames(M1)
```

The columns of $M$ are sorted from most frequent token to least frequent token.  You can specify how many columns ($K$) to keep in $M$ using **KTOKEN**.  The default is $K=500$.

```{r message=FALSE, warning=FALSE}
M1 <- tokenMatrixMaker(text1 , GRAM=2 , KTOKEN=10)
head(M1)
colnames(M1)
```

## Identifying the Dictionary
You can identify a dictionary $S \subseteq \{1,...,K \}$ using LASSO methods.  You can also include other explanatory variables alongisde the tokens (square footage, age, date of sale, etc.).

An example
```{r message=FALSE, warning=FALSE}
X <- as.matrix(cbind(listings$sqft,listings$sqft**2))
text0 <- listings$remarks
text1 <- cleanText(text0)
M <- tokenMatrixMaker(text1 , GRAM=1 , KTOKEN=500)
y <- log(listings$price)
fit <- lassoPostLasso(X,M,y)
```

**lassoPostLasso** includes prediction information
```{r}
fit$predictionInformation
```

**fit** includes the tokens selected by both LASSO procedures
```{r}
head(fit$cvDictionary)
head(fit$hetDictionary)
```

**fit** includes the predicted values for both LASSO procedures
```{r}
head(fit$fittedValues)
```

## realEstateDictionary
The function **realEstateDictionary** is a wrapper for the above procedures.  Simply provide i) a data frame, ii) columns to use in the $X$ matrix, iii) the name of the column that contains the text, iv) the name of the column that includes the dependent variable
```{r}
listings$sqft2 <- listings$sqft**2
listings$logprice <- log(listings$price)
fitWrapper <- realEstateDictionary(XVARS=c("sqft","sqft2"),
                        TEXTVAR="remarks",
                        YVAR="logprice",
                        DATA=listings)
head(fitWrapper$hetDictionary)
```


